### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &1&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all the leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f and OpenSSL 1.1.1.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f}\label{chapter5:tab:RSAOpenSSL1.1.0f}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{llrr}
\hline
\textbf{File}  & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& BN\_num\_bits\_word&*&CF\\
bn\_lib.c& BN\_num\_bits\_word&*&CF\\
bn\_lib.c& BN\_num\_bits\_word&17.2 &DA\\
bn\_lib.c& bn\_correct\_top&*&CF\\
bn\_lib.c& BN\_ucmp&*&CF\\
ct\_b64.c& \_\_udivdi3&5.9 &CF\\
bn\_div.c& BN\_div&*&CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&7.9 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&8.2 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&14.9 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&9.2 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_lib.c& BN\_num\_bits\_word&12.6 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_div.c& BN\_div&17.2 &CF\\
bn\_div.c& BN\_div&11.9 &CF\\
bn\_div.c& BN\_div&3.8 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_asm.c& bn\_sqr\_comba8&*&CF\\
bn\_asm.c& bn\_mul\_comba8&*&CF\\
bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
\hline
\end{tabular}
%}
\renewcommand{\baselinestretch}{1.0}\selectfont
\end{table}
\subsection{Machine Learning Applications}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.

>>>>

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &1&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&8.7& 6.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

We use a fixed RSA blinding value to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all the leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f.  To evaluate the effectiveness of the quantification result, we compare the RSA implementation between OpenSSL 1.1.0 and OpenSSL 1.1.1. Table~\ref{chapter5:tab:RSAOpenSSL1.1.0} shows the summary. Note that \ctool{} can analyze the side-channel leakages at both the byte granularity and the cache line granularity. However, we only show the result in cache line granularity. We compare the result with \tool{}, a symbolic analysis based side-channel quantification tool. \tool{} can tell which line actually leaks the information. So it is possible that one function has several two leakage sites.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0}\label{chapter5:tab:RSAOpenSSL1.1.0}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{llrrc}
\hline
\textbf{File}  & \textbf{Function} & \textbf{\tool{} Result} & \textbf{\ctool{} Result} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& BN\_num\_bits\_word&*&CF & \cmark\\
bn\_lib.c& bn\_correct\_top&*&CF\\
bn\_lib.c& BN\_ucmp&*&CF\\
ct\_b64.c& \_\_udivdi3&5.9 &CF\\
bn\_div.c& BN\_div&*&CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_div.c& BN\_div&17.2 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_asm.c& bn\_sqr\_comba8&*&CF\\
bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
\hline
\end{tabular}
%}
\renewcommand{\baselinestretch}{1.0}\selectfont
\end{table}
\subsection{Machine Learning Applications}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.
